### 2014-06-03 ACL2014/discussion.tex
Updated tex files

Yet another application is removing duplicated instances in a set of suggested results. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries
from the set so that the user is not distracted by duplicated results. Given a set of
we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
in order to find the ``duplicated query terms'' efficiently. 
As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity 
(relatively easier problem) than ``relatedness'', 
we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples. 
The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples-- ``trumbull weather ct'' and ``weather in trumbull ct''.

\section{Conclusion}
\label{sec:conclusion}
To the best of our knowledge, this is the first paper that applies
the vanilla \lsh algorithm of Andoni et al. to the NLP domain. 
We also proposed four novel variants of \lsh that are aimed to reduce the number 
of hash tables used. Two of our variants achieve 
significantly better recall than the vanilla LSH by using the same number of hash tables. 
We also present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial 
large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.

>>>>

Yet another application is removing duplicated instances in a set of suggested results. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries
from the set so that the user is not distracted by duplicated results. Given a set of
we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
in order to find the ``duplicated query terms'' efficiently. 
As ``near-duplicates''  among query terms typically requires ``higher'' degree of similarity 
(relatively easier problem) than ``relatedness'', 
we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples. 
The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples-- ``trumbull weather ct'' and ``weather in trumbull ct''.

\section{Conclusion}
\label{sec:conclusion}
To the best of our knowledge, this is the first paper that applies
the vanilla \lsh algorithm of Andoni et al. to the NLP domain. 
We also proposed four novel variants of \lsh that are aimed to reduce the number 
of hash tables used. Two of our variants achieve 
significantly better recall than the vanilla LSH by using the same number of hash tables. 
We also present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial 
large-scale query logs in sublinear time. On our entire corpus (\dataC) with hundreds of millions of queries, 
\dflipb only requires 3,427 comparisons compared to hundreds of millions of comparisons by exact brute force algorithm.
In future, we will extend our \lsh framework to several large-scale NLP and social media applications.

### 2014-06-03 ACL2014/experiments.tex
updating experiment section
Updated tex files

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
Data & $N$ & $D$  \\ 
\hline
\aol &  $0.3 \times 10^6$  & $0.7 \times 10^6$ \\
\dataA & $6 \times 10^6$  & $66 \times 10^6$ \\
\dataB & $62 \times 10^6$  & $464 \times 10^6$ \\
\dataC &  $617 \times 10^6$  & $ 2.4 \times 10^9$  \\
\hline 
 \end{tabular}
\caption{\footnotesize{Query-logs statistics}}
\label{tab:data}
\end{table}

\subsection{Data}
The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
In addition, a large query log 
from a commercial search engine, denoted as Qlogs, is used for evaluations.
As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates. \dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs. 
For each query $q$, a feature vector in a high dimensional feature space is defined as
$\qvec = (f_1, f_2, \cdots, f_D)$, where $f_i$ is a click through rate of url $i$ and query $q$. Note that in our real implementation, $\qvec$ follows a spare representaion omitting dimensions with zero click through rate.
%For each query $q$, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion). Specifically, each dimension in the feature vector of $q$ corresponds to a weight of a webpage (urls) that have received a user click for $q$. The weight of an url for $q$ is defined as the click through rate of the url.  
Note that in a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our query-log datasets.

\paragraph{Test Data} All the experiments are performed using queries $Q$ randomly sampled from the query logs as the test set of $2000$ queries. 
That is, we want to find set $T$, where $T~=~\{~l~\mid~s(q, q')~\geq~\tau~\}$, $s(q, q')$ is a cosine similiarty, and $q' \in \{\textrm{\dataA}, \textrm{\dataB}, \textrm{\dataC}\}$. 
%For evaluation, we compute the true similar cafor all the $2000$ test queries by calculating cosine similarity 
%between each test query and all the queries in the rest of the dataset. 
For most of the experiments, we set the similarity threshold  $\tau=0.7$.
%meaning that for $q$, candidates $q'$ having  cosine similarity of larger than or equal to $0.7$ are retrieved.

\paragraph{Evaluation Metrics}
We use two metrics for evaluation: recall and number of comparisons. 
Recall of an LSH algorithm is to measure how much the algorithm is able to retrieve \emph{true} similar candidates
%, which tells how (found using candidates returned by computing exact cosine similarity) 
that is retrieved by the LSH algorithm.  
The number of comparisons performed by an algorithm is computed as the average number of pairwise comparisons that is done per test query. 
The goal of this paper is to maximize recall and to minimize the number of comparisons.

\subsection{Evaluating Vanilla LSH} 
\label{subsec:eval:vanillaLSH}

\begin{table}
\centering
\begin{tabular}{|c|rc|rc|}
\hline
\multirow{2}{*}{$\tau$}  & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
\hline
0.7 & \multirow{3}{*} {57}  & .63  & \multirow{3}{*} {1052} & .67 \\
0.8 &   & .84  &  & .81 \\
0.9 &   & .98  &  & .96 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $\tau$ with fixed $K=16$ and $L=10$ on \aol and \dataA.}}
\label{tab:varyTau}
\end{table}

In the first experiment, we vary the similarity threshold parameter $\tau$ to be in $\{0.7,0.8,0.9\}$ 
while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
Table~\ref{tab:varyTau} shows that $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
This is expected as finding near duplicates is easier than finding near neighbors. For, rest of this paper, 
we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors for our test queries.

In the second experiment, we vary $L$ to be in $\{1,10,28,55\}$ while fixing $K=16$ on the \aol and \dataA datasets. 
Recall that $L$ denotes the number of hash tables and $K$ is the width of the index of the buckets in the table. 
Increasing $K$ results in increase of the precision by reducing the false positive candidates, but 
the $L$ also need to be correspondingly increased in order the maintain a good recall
(i.e. reduce false negatives). 
Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
but at the expense of performing more comparisons on both the datasets. 
In addition, having a large $L$ 
means generating large number of random projection bits and hash tables which is 
both time and memory intensive. Hence, we fix $L=10$, 
which leads to a reasonable recall with a tolerable number of comparisons.

\begin{table}
\centering
\begin{tabular}{|c|rc|rc|}
\hline
\multirow{2}{*}{L} & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
\hline
1 & 7  & .28 & 106 & .36 \\
 \rowcolor[gray]{0.9} 10  &  57 & .63 & 1052 & .67 \\
28 &  152 & .77 & 2908 & .78 \\
55 &  297 & .89 & 5648 & .84 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $L$ with fixed $K=16$ on \aol and \dataA with $\tau=0.7$.}}
\label{tab:varyL}
\end{table}
In the third experiment, we vary $K$ to be in $\{4,8,16\}$ while fixing $L=10$ on \aol and \dataA datasets. 
As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
comparisons and worsens recall on both the datasets. This is intuitive as  
the larger value of $K$ leads to larger 
gap between probabilities of collision between close queries 
and far queries (see Section \ref{sec:vlsh}). 
Hence, we fix $K=16$ to have few number of comparisons.

\begin{table}
\centering
%\begin{tabular}{|c|r|c|}
\begin{tabular}{|c|rc|rc|}
\hline
%$K$ & Comparisons & Recall \\
\multirow{2}{*}{K} & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 &{\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}   \\
\hline
4  &  112,347 & .98 & 2,29,2670 & .96 \\
8 &  11,008 & .90 & 221,132 & .88 \\
\rowcolor[gray]{0.9}16 &  57 & .63 & 1,052 & .67 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
\label{tab:varyK}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|c|r|c|}
\hline
Data & Comparisons & Recall \\
\hline
\aol & 57  & .63 \\
\dataA  &  1,052 & .67 \\
\dataB    & 10,515 & .64 \\
\dataC    & 105,126 & - \\
\hline 
 \end{tabular}
\caption{\footnotesize{Fixed $K=16$  and $L=10$ on different sized datasets with $\tau=0.7$.}}
\label{tab:varyData}
\end{table}

\begin{table}
\centering
\begin{tabular}{|c|r|c|}
\hline
{\small Data} & {\small Comparisons} & {\small Recall} \\
\hline
\aol  ($K=16$) & 57  & .63 \\
\dataA ($K=16$)  &  1,052 & .67 \\
\dataB ($K=20$)   & 695 & .53 \\
\dataC ($K=24$)   & 464 & - \\
\hline 
 \end{tabular}
\caption{\footnotesize{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ on different sized datasets.}}
\label{tab:bestLSH}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\rflipq} & \multicolumn{2}{c|}{\dflipq}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 108 & .65 & 106 & .72 \\
2 & 159 & .66 &  {\it155} & {\bf .75}  \\
5 &  311 & .70 &  303 &  .79  \\
10 & 557  & .75 &  552 &  .81  \\
16 & 839   & .82 &  839 &  .82  \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Flipping the bits in the query only with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:query:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\rflipb} & \multicolumn{2}{c|}{\dflipb}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 204 & .71 & 192 & .80 \\
 2 & 433 & .73    &  {\it 405} & {\bf .86}  \\
5 &  1557 & .86  & 1475 & .93     \\
10 &  4138 & .94 & 4059 & .96     \\
16 &  5922 & .96 & 5922 & .96     \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Flipping the bits in both the query and the database with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:both:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\dflipq} & \multicolumn{2}{c|}{\dflipb}   \\
\hline
{\small Data} & {\small Comps.} & {\small Recall}  & {\small Comps.} & {\small Recall} \\
\hline
{\small \aol ($K=16$)} & 155 & .75 & 405 & .86 \\
{\small \dataA ($K=16$)} & 2980 & .76  & 7904  & .84   \\
{\small \dataB ($K=20$)} & 1954  & .64 & 5242  & .72     \\
{\small \dataC ($K=24$)} & 1280  & -  & 3427 & -      \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ and $F=2$ on different sized datasets with $\tau=0.7$.}}
\label{tab:dataset:final}
\end{table}

@@

\subsection{Evaluating Multi-Probe LSH}
\label{subsec:eval:multiProbeLSH}
In the first experiment, we compare flipping the bits in query only. 
We evaluate two approaches: \rflipq and \dflipq. We can make several observations from Table \ref{tab:query:aol}: 1) As expected, increasing the number of flips improve recall at expense of more comparisons for both \dflipq and \rflipq. 2) The last row of the Table \ref{tab:query:aol} shows that once we flip all the $K$ bits ($F=16$),  \dflipq and \rflipq converge to the same algorithm.  3) Our results show that \dflipq has significantly better recall than \rflipq with similar number of comparisons. In second row of the table with $F=2$, \dflipq has nine points better recall than \rflipq.

>>>>

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
Data & $N$ & $D$  \\ 
\hline
\aol &  $0.3 \times 10^6$  & $0.7 \times 10^6$ \\
\dataA & $6 \times 10^6$  & $66 \times 10^6$ \\
\dataB & $62 \times 10^6$  & $464 \times 10^6$ \\
\dataC &  $617 \times 10^6$  & $ 2.4 \times 10^9$  \\
\hline 
 \end{tabular}
\caption{\small{Query-logs statistics}}
\label{tab:data}
\end{table}

\subsection{Data}
The first data set is the one made available to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
In addition, a large query log 
from a commercial search engine, denoted as Qlogs, is used for evaluations.
As Qlogs typically reaches to hundreds of millions of queries over multiple days 
(i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive 
set of queries posed to the search engine.}.) We then generated multiple 
datasets from Qlogs by sampling at various size rates. \dataA represents 
a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs. 
For each query $q$, a feature vector in a high dimensional feature space is defined as
$\qvec = (f_1, f_2, \cdots, f_D)$, where $f_i$ is a click through rate of url $i$ and query $q$. 
Note that in our real implementation, $\qvec$ is represented as a spare feature vector with only non-zero click through rate features. 
%For each query $q$, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion). Specifically, each dimension in the feature vector of $q$ corresponds to a weight of a webpage (urls) that have received a user click for $q$. The weight of an url for $q$ is defined as the click through rate of the url.  
In a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our query-log datasets.

\paragraph{Test Data} All the experiments are performed using queries $Q$ randomly sampled from the query logs as the test set of $2000$ queries. 
That is, we want to find set $T$, where $T~=~\{~l~\mid~s(q, q')~\geq~\tau~\}$, $s(q, q')$ is a cosine similarity, and $q' \in \{\textrm{\dataA}, \textrm{\dataB}, \textrm{\dataC}\}$. 
%For evaluation, we compute the true similar cafor all the $2000$ test queries by calculating cosine similarity 
%between each test query and all the queries in the rest of the dataset. 
For most of the experiments, we set the similarity threshold  $\tau=0.7$.
%meaning that for $q$, candidates $q'$ having  cosine similarity of larger than or equal to $0.7$ are retrieved.

\paragraph{Evaluation Metrics}
We use two metrics for evaluation: recall and number of comparisons. 
Recall of an \lsh algorithm is to measure how much the algorithm is able to retrieve \emph{true} similar candidates
%, which tells how (found using candidates returned by computing exact cosine similarity) 
that is retrieved by the \lsh algorithm.  
The number of comparisons performed by an algorithm is computed as the average number of pairwise comparisons that is done per test query. 
The goal of this paper is to maximize recall and to minimize the number of comparisons.

\subsection{Evaluating Vanilla \lsh} 
\label{subsec:eval:vanillaLSH}

\begin{table}
\centering
\begin{tabular}{|c|rc|rc|}
\hline
\multirow{2}{*}{$\tau$}  & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
\hline
0.7 & \multirow{3}{*} {57}  & .63  & \multirow{3}{*} {1052} & .67 \\
0.8 &   & .84  &  & .81 \\
0.9 &   & .98  &  & .96 \\
\hline 
 \end{tabular}
\caption{\small{Varying $\tau$ with fixed $K=16$ and $L=10$ on \aol and \dataA.}}
\label{tab:varyTau}
\end{table}

In the first experiment, we vary the similarity threshold parameter $\tau$ to be in $\{0.7,0.8,0.9\}$ 
while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
Table~\ref{tab:varyTau} shows that $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
This is expected as finding near duplicates is easier than finding near neighbors. For the rest of this paper, 
 $\tau$ is set as $0.7$ since we are interested in both near-duplicates and nearest-neighbors for our test queries.

In the second experiment, we vary $L$ to be in $\{1,10,28,55\}$ while fixing $K=16$ on the \aol and \dataA datasets. 
Recall that $L$ denotes the number of hash tables and $K$ is the width of the index of the buckets in the table. 
Increasing the $K$ results in increase of the precision by reducing the false positive candidates, but 
$L$ also need to be correspondingly increased in order to maintain a good recall
(i.e. reduce false negatives). 
Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
but at the expense of conducting more comparisons on both the datasets. 
In addition, having a large $L$ 
means generating large number of random projection bits and hash tables which is 
both time and memory intensive. Hence, we fix $L=10$, 
which leads to a reasonable recall with a tolerable number of comparisons.

\begin{table}
\centering
\begin{tabular}{|c|rc|rc|}
\hline
\multirow{2}{*}{L} & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
\hline
1 & 7  & .28 & 106 & .36 \\
 \rowcolor[gray]{0.9} 10  &  57 & .63 & 1052 & .67 \\
28 &  152 & .77 & 2908 & .78 \\
55 &  297 & .89 & 5648 & .84 \\
\hline 
 \end{tabular}
\caption{\small{Varying $L$ with fixed $K=16$ on \aol and \dataA with $\tau=0.7$.}}
\label{tab:varyL}
\end{table}
In the third experiment, we vary $K$ to be in $\{4,8,16\}$ while fixing $L=10$ on \aol and \dataA datasets. 
As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
comparisons and worsens recall on both the datasets. This is intuitive as  
the larger value of $K$ leads to larger 
gap between probabilities of collision between close queries 
and far queries (see Section \ref{sec:vlsh}). 
Hence, we fix $K=16$ to have few number of comparisons.

\begin{table}
\centering
%\begin{tabular}{|c|r|c|}
\begin{tabular}{|c|rc|rc|}
\hline
%$K$ & Comparisons & Recall \\
\multirow{2}{*}{K} & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 &{\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}   \\
\hline
4  &  112,347 & .98 & 2,29,2670 & .96 \\
8 &  11,008 & .90 & 221,132 & .88 \\
\rowcolor[gray]{0.9}16 &  57 & .63 & 1,052 & .67 \\
\hline 
 \end{tabular}
\caption{\small{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
\label{tab:varyK}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|r|c|}
\hline
Data & Comparisons & Recall \\
\hline
\aol & 57  & .63 \\
\dataA  &  1,052 & .67 \\
\dataB    & 10,515 & .64 \\
\dataC    & 105,126 & - \\
\hline 
 \end{tabular}
\caption{\small{Fixed $K=16$  and $L=10$ on different sized datasets with $\tau=0.7$.}}
\label{tab:varyData}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{|c|r|c|}
\hline
{\small Data} & {\small Comparisons} & {\small Recall} \\
\hline
\aol  ($K=16$) & 57  & .63 \\
\dataA ($K=16$)  &  1,052 & .67 \\
\dataB ($K=20$)   & 695 & .53 \\
\dataC ($K=24$)   & 464 & - \\
\hline 
 \end{tabular}
\caption{\small{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ on different sized datasets.}}
\label{tab:bestLSH}
\end{table}

\begin{table}[h]
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\rflipq} & \multicolumn{2}{c|}{\dflipq}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 108 & .65 & 106 & .72 \\
2 & 159 & .66 &  {\it155} & {\bf .75}  \\
5 &  311 & .70 &  303 &  .79  \\
10 & 557  & .75 &  552 &  .81  \\
16 & 839   & .82 &  839 &  .82  \\
\hline 
 \end{tabular}
 }
\caption{\small{Flipping the bits in the query only with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:query:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\rflipb} & \multicolumn{2}{c|}{\dflipb}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 204 & .71 & 192 & .80 \\
 2 & 433 & .73    &  {\it 405} & {\bf .86}  \\
5 &  1557 & .86  & 1475 & .93     \\
10 &  4138 & .94 & 4059 & .96     \\
16 &  5922 & .96 & 5922 & .96     \\
\hline 
 \end{tabular}
 }
\caption{\small{Flipping the bits in both the query and the database with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:both:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\dflipq} & \multicolumn{2}{c|}{\dflipb}   \\
\hline
{\small Data} & {\small Comps.} & {\small Recall}  & {\small Comps.} & {\small Recall} \\
\hline
{\small \aol ($K=16$)} & 155 & .75 & 405 & .86 \\
{\small \dataA ($K=16$)} & 2980 & .76  & 7904  & .84   \\
{\small \dataB ($K=20$)} & 1954  & .64 & 5242  & .72     \\
{\small \dataC ($K=24$)} & 1280  & -  & 3427 & -      \\
\hline 
 \end{tabular}
 }
\caption{\small{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ and $F=2$ on different sized datasets with $\tau=0.7$.}}
\label{tab:dataset:final}
\end{table}

@@

\subsection{Evaluating Multi-Probe \lsh}
\label{subsec:eval:multiProbeLSH}
In the first experiment, we compare flipping the bits in query only. 
We evaluate two approaches: \rflipq and \dflipq. We can make several observations from Table \ref{tab:query:aol}: 1) As expected, increasing the number of flips improve recall at expense of more comparisons for both \dflipq and \rflipq. 2) The last row of the Table \ref{tab:query:aol} shows that once we flip all the $K$ bits ($F=16$),  \dflipq and \rflipq converge to the same algorithm.  3) Our results show that \dflipq has significantly better recall than \rflipq with similar number of comparisons. In second row of the table with $F=2$, \dflipq has nine points better recall than \rflipq.

### 2014-06-03 ACL2014/relatedwork.tex
Updated tex files

The next major difference between our research and existing work is that the 
existing work deals with approximating cosine similarity by Hamming distance  
\cite{ravichandran05,vandurme-lall:2010:Short,vandurme-lall:2011:Short,goyal12Flag}. 
In that problem setting, the goal is to minimize both false positives and negatives. 
In our work, we focus on minimizing false negatives with zero tolerance for false positives.

>>>>

The next major difference between our research and existing work is that the 
existing work deals with approximating cosine similarity by Hamming distance  
\cite{ravichandran05,vandurme-lall:2010:Short,vandurme-lall:2011:Short,goyal12Flag,moranACL13}. Moran et al. \shortcite{moranACL13} recently proposed a data-driven non-uniform bit allocation across hyperplanes that uses less bits than many existing \lsh schemes to approximate cosine similarity by Hamming distance.     
In all these existing problem settings, the goal is to minimize both false positives and negatives. However, we focus on minimizing false negatives with zero tolerance for false positives.

### 2014-06-03 ACL2014/system.tex
Updated tex files

\begin{figure}[ht]
%\small
\fbox{
\begin{minipage}{2.5in}
{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
All queries with the same $g_j$ value ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

@@

In this work, we have implemented the above algorithm in a map-reduce setting (Hadoop).  
In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implementation scales to hundreds of millions of queries.

@@

>>>>

\begin{figure}[ht]
\small
\fbox{
\begin{minipage}{2.5in}
{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
All queries with the same $g_j$ value ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

@@

In this work, we have implemented the above algorithm in a map-reduce setting (Hadoop). 
\lsh algorithm is incredibly easy to implement in map-reduce setting; hence due to limited space, 
we do not include the unnecessary implementation details of this algorithm.  
In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implementation scales to hundreds of millions of queries.

@@

In this work, we have implemented all the above four variants of \lsh in a map-reduce setting (Hadoop). 
It is incredibly easy to change the existing vanilla \lsh map-reduce implementation to implement 
these four novel variants of \lsh.  
In Section \ref{subsec:eval:multiProbeLSH}, we show that the map-reduce implementation of four novel variants of \lsh scales to hundreds of millions of queries.
